\LARGE \bf Multi-Armed Bandit Models for 2D Grasp Planning with Uncertainty

### 2015-06-15 paper.tex
.

\section{Simulation Experiments}
We used the Brown Vision Lab 2D dataset \cite{brown} of 2D objects as in \cite{christopoulos2007handling}.
We downsampled the silhouette by a factor of 2 to create a 40 x 40 occupancy map, which holds 1 if the point cloud was
observed and 0 if it was not observed, and a measurement noise map, which holds the variance of 0-mean noise added to the SDF values.
The measurement noise was assigned uniformly at random to the SDF.
We then construct a GPIS using the same method as proposed in~\cite{mahler2015gp}.
The noise in approach, pose, and friction coefficient were set to the following variances $\sigma_{\psi}^2 = 0.2$ rads$^2$, $\sigma_{\by}^2 = 3$ grid cells$^2$, $\sigma_{\mu}^2 = 0.4$, $\sigma_{\phi}^2 = 0.3$ rads$^2$ and $\sigma_{\bt}^2 = 3$ grid cells$^2$.
We  performed experiments for the case of two hard contacts in 2-D.
We drew random grasps $\Gamma$ by uniformly sampling the angle of the grasp axis around a circle with radius $\sqrt{2}
M$, where $M$ is the dimension of the workspace, and then sampling the circle's origin from a zero mean Gaussian with
variance 10 units$^2$. All experiments were run on a machine with OS X with a 2.7 GHz Intel core i7 processor and 16 GB
1600 MHz memory in Matlab 2013b. 
Figure \ref{fig:shape_samples} displays examples of GPIS models using the GPIS-Blur method~\cite{mahler2015gp}
as well as resulting grasp samples.

\subsection{Multi-Armed Bandit Experiments}
For our experiments we consider selecting an optimal grasp among $|G| = 1000$ candidates per object. We draw samples from our
graphical model using the technique described in Sec.  \ref{sec:grasp_sample}. We calculated the expected performance
over 100 randomly selected shapes in the Brown Vision Lab 2D dataset and for the grasps planned by Thompson sampling,
Gittins indices, iterative pruning~\cite{kehoe2012toward} and uniform allocation. Uniform allocation selects a grasp at
random from the set to sample the next candidate and thus does not use any prior information. Iterative pruning prunes
grasps every 1000 iterations based on lowest sample mean and removes 10$\%$ of the current grasp set.  We set the
discount factor $\gamma =0.98$ for the Gittins method, which was the highest we could compute in a reasonable amount of
time due to the exponential growth in computation time with respect to $\gamma$~\cite{gittins2011multi}.

In Fig. \ref{fig:grasp_quality}, we plot time $t$ vs. $P(\Gamma_{\bar{k},t})$/$P(\Gamma^*)$, the normalized probability
of force closure for the grasp returned by the algorithm.  Non-MAB methods such as uniform sampling and iterative
pruning (eliminating candidates grasp based on sample mean) eventually converge to within 3$\%$ of the optimal grasp,
requiring approximately 40,000 and 20,000 iterations.  Gittins indices and Thompson sampling  perform significantly
better, converging after only 4000 iterations. In Fig. \ref{fig:shape_samples}, we select a stopping time $T_s=10,000$,
which corresponds to 10 samples per grasp on average, and for each method visualize the grasp  returned, $\Gamma_{\bar{k},10,000}$, on two real world objects, a coaxial cable splitter and a mechanical switch.

The time per iteration is $t_{i} = t_{a}+t_{p}$, where $t_{a}$ is the time to decide which arm to pull next and $t_{p}$ is the time taken to draw a sample from the graphical model in Fig. \ref{fig:graphical_model}. The time per iteration for Thompson sampling, Gittins indices, iterative pruning and uniform allocation is $31.6$, $31.2$, $30.4$ and $30.2$ ms. Most of $t_{i}$ is dominated by sampling time, since $t_{p} \approx 30$ms. Sampling from our graphical model in Fig. \ref{fig:graphical_model} involves drawing samples form a GPIS, a high dimensional Gaussian, and evaluating the probability of force closure metric. 
The MAB algorithm can also be terminated when the $95\%$ confidence interval around the returned grasp (see Equation \ref{eq:confidence}) is below a set threshold $\epsilon$. We plot the algorithm's confidence intervals around the returned grasp $P_F(\Gamma_{\bar{k}})$ vs. the number of samples drawn in Fig. \ref{fig:confidence} for the Gittins indices, Thompson sampling, iterative pruning~\cite{kehoe2012toward} and uniform allocation.  As illustrated, the confidence interval for Thompson sampling and Gittins indices converges at a faster rate than the other two methods.

@@

\begin{figure*}%
\label{fig:shape_examples}
    \centering
    \includegraphics[width=16.5cm]{figures/shapes.jpg}%
    \caption{Grasps with the highest estimated probabilty of force closure $P_F$ after 10,000 samples using uniform allocation, iterative pruning, Gittins indices, and Thompson sampling on two objects, a coaxial cable splitter and a mechanical switch. For reference, we also show the grasp with highest $P_F$ after brute force evaluation using 100,000 samples and the nominal shape. The candidate grasp set was of size $|\mG|=1000$. We visualize the GPIS representation of the object shape uncertainty using GPIS-Blur~\cite{mahler2015gp}, which causes more uncertain areas to appear more blurry.}%
    \label{fig:shape_samples}%
\end{figure*}

@@

For the friction coefficient, we varied $\sigma^2_{\mu}$ across the values $\lbrace 0.05, 0.2, 0.4 \rbrace$.
As illustrated in Table 1, the performance of the bandit algorithm remains largely unchanged, with typical convergence to zero in simple regret less than 5000 evaluations.

>>>>

\section{Simulation Experiments}
We used the Brown Vision Lab 2D dataset \cite{brown} of 2D objects as in \cite{christopoulos2007handling}.
We downsampled the silhouette by a factor of 2 to create a 40 x 40 occupancy map, which contained 1 if the object was
observed and 0 if it was not observed. We computed a quadtree representation of the SDF and removed information about
the SDF on grid cells corresponding to uniformly chosen quadtree cells to simulate localized uncertainty in shape perception.
We then construct a GPIS using the same method as proposed in~\cite{mahler2015gp}.
The noise parameters in approach, pose, and friction coefficient were set to the following variances: $\sigma_{\psi}^2 = 0.2$ rads$^2$, $\sigma_{\by}^2 = 3$ grid cells$^2$, $\sigma_{\mu}^2 = 0.4$, $\sigma_{\phi}^2 = 0.3$ rads$^2$ and $\sigma_{\bt}^2 = 3$ grid cells$^2$.
We  performed experiments for the case of two hard contacts in 2-D.
We drew random grasps $\Gamma$ by uniformly sampling the angle of the grasp axis around a circle with radius $\sqrt{2}
M$, where $M$ is the dimension of the workspace, and then sampling the circle's origin from a zero mean Gaussian with
variance 10 units$^2$. All experiments were run on a machine with OS X with a 2.7 GHz Intel core i7 processor and 16 GB
1600 MHz memory in Matlab 2013b. 
Figure \ref{fig:shape_samples} displays examples of GPIS models using the GPIS-Blur method~\cite{mahler2015gp}
as well as resulting grasp samples.

\subsection{Multi-Armed Bandit Experiments}
For our experiments, we consider selecting an optimal grasp among $|G| = 1000$ candidates per object. We draw samples from our
graphical model using the technique described in Sec.  \ref{sec:grasp_sample}. We calculated the expected performance
over 100 randomly selected shapes in the Brown Vision Lab 2D dataset and for the grasps planned by Thompson sampling,
Gittins indices, iterative pruning~\cite{kehoe2012toward} and uniform allocation. Uniform allocation selects a grasp at
random from the set to sample the next candidate and thus does not use any prior information. Iterative pruning prunes
grasps every 1000 iterations based on lowest sample mean and removes 10$\%$ of the current grasp set.  We set the
discount factor $\gamma =0.98$ for the Gittins method, which was the highest we could compute in a reasonable amount of
time due to the exponential growth in computation time with respect to $\gamma$~\cite{gittins2011multi}.

In Fig. \ref{fig:grasp_quality}, we plot time $t$ vs. $P(\Gamma_{\bar{k},t})$/$P(\Gamma^*)$, the normalized probability
of force closure for the grasp returned by the algorithm.  Non-MAB methods such as uniform sampling and iterative
pruning (eliminating candidates grasp based on sample mean) eventually converge to within 3$\%$ of the optimal grasp,
requiring approximately 40,000 and 20,000 iterations.  Gittins indices and Thompson sampling  perform significantly
better, converging after only 4000 iterations. In Fig. \ref{fig:shape_samples}, we select a stopping time $T_s=10,000$,
which corresponds to 10 samples per grasp on average, and for each method visualize the grasp returned,
$\Gamma_{\bar{k},10,000}$.

The time per iteration is $t_{i} = t_{a}+t_{p}$, where $t_{a}$ is the time to decide which arm to pull next and $t_{p}$ is the time taken to draw a sample from the graphical model in Fig. \ref{fig:graphical_model}. The time per iteration for Thompson sampling, Gittins indices, iterative pruning and uniform allocation is $31.6$, $31.2$, $30.4$ and $30.2$ ms. Most of $t_{i}$ is dominated by sampling time, since $t_{p} \approx 30$ ms. Sampling from our graphical model in Fig. \ref{fig:graphical_model} involves drawing samples form a GPIS, a high dimensional Gaussian, and evaluating the probability of force closure metric. 
The MAB algorithm can also be terminated when the $95\%$ confidence interval around the returned grasp (see Equation
\ref{eq:confidence}) is below a set threshold $\epsilon$ in size. We plot the algorithm's confidence intervals around the returned grasp $P_F(\Gamma_{\bar{k}})$ vs. the number of samples drawn in Fig. \ref{fig:confidence} for the Gittins indices, Thompson sampling, iterative pruning~\cite{kehoe2012toward} and uniform allocation.  As illustrated, the confidence interval for Thompson sampling and Gittins indices converges at a faster rate than the other two methods.

@@

\begin{figure*}%
\label{fig:shape_examples}
    \centering
    \includegraphics[width=16.5cm]{figures/shapes.jpg}%
    \caption{Grasps with the highest estimated probabilty of force closure $P_F$ after 10,000 samples using uniform
    allocation, iterative pruning, Gittins indices, and Thompson sampling on two objects from the Brown 2D dataset
\cite{brown}. For reference, we also show the grasp with highest $P_F$ after brute force evaluation using 100,000
samples and the nominal shape. The candidate grasp set was of size $|\mG|=1000$ for each object. We visualize the GPIS
representation of the imposed object shape uncertainty using GPIS-Blur~\cite{mahler2015gp}, which causes more uncertain areas to appear more blurry.}%
    \label{fig:shape_samples}%
\end{figure*}

@@

For the friction coefficient, we varied $\sigma^2_{\mu}$ across the values $\lbrace 0.05, 0.2, 0.4 \rbrace$.
As illustrated in Table 1, the performance of the bandit algorithm remains largely unchanged, with typical convergence
to zero in simple regret in less than 5000 iterations.
